Suplementary Material 2: Drawing Publication Plots

### 2023-03-23 S2_draw_publication_plots.Rmd
fix plot appearence

```{r}
library(ggplot2)
#some nice colors
bc <- c("purple", "black", "navy", "darkgoldenrod2", "springgreen3", "gray")

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="EE all"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="EE all", fill = "EE all"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="orig. rural"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="orig. rural"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = "(A) With last chidren",
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8, legend_pos = c(0.7,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "dataset")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="EE all"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="EE all", fill = "EE all"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="orig. rural"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="orig. rural"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    labs(subtitle = "(B) Without last children",
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "dataset")

p3 
```
```{r, fig.height=8, fig.width=6}
p2_mod <- p2+theme(axis.text.x = element_blank(), axis.title.x = element_blank())
p3_mod <- p3
plot_1 <- gridExtra::grid.arrange(p2_mod, p3_mod, nrow=2)
```

>>>>

```{r}
library(ggplot2)
#some nice colors
bc <- c( "azure3","purple4", "navy", "darkgoldenrod2", "springgreen3", "black")

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="8 European populations"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European populations"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = "(A) Complete datasets",
         y="Per-birth twinning probability",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
   scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="8 European populations"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European populations"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    labs(subtitle = "(B) Without last births",
         y="Per-birth twinning probability",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

p3 
```
```{r, fig.height=11.7, fig.width=8.3}
p2_mod <- p2
p3_mod <- p3 +theme( axis.title.y = element_blank())
plot_1 <- gridExtra::grid.arrange(p2_mod, p3_mod, ncol=2, nrow=2)
```
```{r}
#export A4 plot
ggplot2::ggsave("./exports/figure_1_mother_level_data_twinnig_prob.pdf",
                plot_1, height=11.7, width=8.3)
ggplot2::ggsave("./exports/figure_1_mother_level_data_twinnig_prob.svg",
                plot_1, height=11.7, width=8.3)
```
